Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-03 Paper.tex
Start o JS API

Yet TODO.
\end{document}

>>>>

To make an \DH{}App work with on Ethereum, you'll need to know about the Ethereum Javascript bindings, or, if you like, magic Javascript objects.

There is currently only one such object; the \texttt{eth} object.

Parameters

Parameters are, in general, strings which are interpreted according to the required type. When converting between integers and hashes/byte-arrays, it is interpreted as a big-endian as is standard for Ethereum. The following forms are allowed; they are all interpreted in the same way:
%
%"ABC"
%"0x414243"
%"4276803"
%In each case, they are interpreted as the number 4276803. The first two values may be alternated between with bin() and unbin().
%
%Such byte-arrays may be concatenated with the + operator as is normal for strings.
%
%Strings also have a number of additional methods to help with conversion and alignment when switching between addresses, 256-bit integers and free-form byte-arrays for transaction data:
%
%bin(): Converts the string to binary format.
%pad(a, b): Converts the string to binary format (ready for data parameters) and pads with zeroes on the left size until it is of width a. Then pads with zeroes on the right side until it has grown to size b. If b is less that the width of the string, it is resized accordingly.
%pad(l): Converts the string to binary format (ready for data parameters) and pads with zeroes until it is of width l. Will pad to the left if the original string is numeric, or to the right if binary. If l is less than the width of the string, it is resized accordingly.
%unbin(): Converts the string from binary format to hex format.
%unpad(): Converts the string from binary format to hex format, first removing any zeroes from the right side.
%eth
%
%Properties: For each such item, there is also an asynchronous method, taking a parameter of the callback function, itself taking a single parameter of the property's return value and of the same name but prefixed with get and recapitalised, e.g. getCoinbase(_fn).
%
%coinbase Returns the coinbase address of the client.
%isListening Returns true if and only if the client is actively listening for network connections.
%isMining Returns true if and only if the client is actively mining new blocks.
%gasPrice Returns the special 256-bit number equal to the hard-coded testnet price of gas.
%key Returns the special key-pair object corresponding to the preferred account owned by the client.
%keys Returns a list of the special key-pair objects corresponding to all accounts owned by the client.
%peerCount Returns the number of peers currently connected to the client.
%Synchronous Getters: For each such item, there is also an asynchronous method, taking an additional parameter of the callback function, itself taking a single parameter of the synchronous method's return value and of the same name but prefixed with get and recapitalised, e.g. getBalanceAt(_a, _fn).
%
%balanceAt(_a) Returns the balance of the account of address given by the address _a.
%storageAt(_a, _x) Returns the value in storage at position given by the number _x of the account of address given by the address _a.
%txCountAt(_a) Returns the number of transactions send from the account of address given by _a.
%isContractAt(_a) Returns true if the account of address given by _a is a contract-account.
%Transactions
%
%create(_sec, _xEndowment, _bCode, _xGas, _xGasPrice, _fn) Creates a new contract-creation transaction, given parameters:
%_sec, the secret-key for the sender;
%_xEndowment, the number equal to the contract's endowment;
%_bCode, the byte-array EVM-bytecode for the initialisation of the contract;
%_xGas, the number equal to the amount of gas to purchase for the transaction (unused gas is refunded); and
%_xGasPrice, the number equal to the price of gas for this transaction. Returns the special address object representing the new contract's account.
%_fn, the callback function, called on completion of the transaction.
%transact(_sec, _xValue, _aDest, _bData, _xGas, _xGasPrice, _fn) Creates a new message-call transaction, given parameters:
%_sec, the secret-key for the sender;
%_xValue, the value transferred for the transaction (in Wei);
%_aDest, the address representing the destination address of the message;
%_bData, the byte array containing the associated data of the message;
%_xGas, the amount of gas to purchase for the transaction (unused gas is refunded); and
%_xGasPrice, the price of gas for this transaction.
%_fn, the callback function, called on completion of the transaction.
%Events
%
%watch(_a, _fn): Registers _fn as a callback for whenever anything about the given address's state changes, and also on the initial load.
%watch(_a, _x, _fn): Registers _fn as a callback for whenever the given storage location of the given address changes, and also on the initial load.
%newBlock(_fn): Registers _fn as a callback for whenever the state changes, and also on the initial load.
%Misc
%
%secretToAddress(_a): Determines the address from the secret key _a.

\end{document}
